Review of Assigned Readings

### 2018-01-05 paper/paper.tex
added and sorted acronyms, added footnotes

\section*{List of Abbreviation} 
\begin{acronym}[ASECRETTT]
\acro{VAR}{Vector Autoregression}
\acro{EMH}{Efficient Market Hypothesis}
\acro{etc}{et cetera}
\end{acronym}

@@

As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of Bitcoin and the frequency of Bitcoin topics on Twitter. The goal should be reached by answering the following research question: \\
To what extent does the amount of Twitter tweets about Bitcoin has an effect on the price movement of Bitcoin?

@@

%************************** Chapter 3 - Econometric Modelling and Results **************************
\section{Econometric Modelling and Results}
\label{sec:EconometricModellingandResults}
As stated in the beginning, our purpose is to examine the underlying relationship between the number of tweets containing "Bitcoin" and Bitcoin price fluctuations. From our data collection, we are left with two time series datasets representing two variables. A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach. In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
To generate the following econometric results we used the statistical software STATA.

@@

We shall test the stationarity for the "crude" Twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference Twitter data (df\_nr\_of\_tweets) and the logarithmic first difference one (log\_df\_nr\_of\_tweets). The results of the augmented Dickey-Fuller test are listed in the following table:\\

@@

\subsection{Preparing for VAR: Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria measure the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}). The calculations of these criteria for our specific data set are shown in the following table.\\

@@

As can be seen, STATA calculates and presents various information criteria (AIC: Akaike Information Criterion, HQIC: Hannan–Quinn information criterion, SBIC: Schwarz-Bayesian Information Criterion). The asterisk indicates the optimal lag lenght to use for the regression analysis. In this case all criteria suggest a lag length of 1.

>>>>

\section*{List of Abbreviations} 
\begin{acronym}[ASECRETTT]
\acro{ADF}{Augmented Dickey-Fuller}
\acro{AIC}{Akaike Information Criterion}
\acro{EMH}{Efficient Market Hypothesis}
\acro{etc}{et cetera}
\acro{HQIC}{Hannan–Quinn information criterion}
\acro{SBIC}{Schwarz-Bayesian Information Criterion}
\acro{VAR}{Vector Autoregression}
\end{acronym}

@@

As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of Bitcoin and the frequency of Bitcoin topics on Twitter. The goal should be reached by answering the following research question: \\
To what extent does the amount of Twitter tweets about Bitcoin correlate with the price movement of Bitcoin?

@@

%************************** Chapter 3 - Econometric Modelling and Results **************************
\section{Econometric Modelling and Results}
\label{sec:EconometricModellingandResults}
As stated in the beginning, our purpose is to examine the underlying relationship between the number of tweets containing "Bitcoin" and Bitcoin price fluctuations. From our data collection, we are left with two time series datasets representing two variables. A broadly used statistical method to simultaneously analyse multiple time series is the Vector Autoregression (VAR) approach. In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
To generate the following econometric results we used the statistical software STATA.

@@

We shall test the stationarity for the "crude" Twitter data (variable name: nr\_of\_tweets), and since the variable may not pass the stationarity test, we also check for the stationarity of the first difference Twitter data (df\_nr\_of\_tweets) and the logarithmic first difference one (log\_df\_nr\_of\_tweets). The results of the augmented Dickey-Fuller (ADF) test are listed in the following table:\\

@@

\subsection{Preparing for VAR: Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria measure the trade-off between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}). The calculations of these criteria for our specific data set are shown in the following table.\\

@@

As can be seen, STATA calculates and presents various information criteria (AIC\footnote{Akaike Information Criterion}, HQIC\footnote{Hannan–Quinn information criterion}, SBIC\footnote{Schwarz-Bayesian Information Criterion}). The asterisk indicates the optimal lag length to use for the regression analysis. In this case all criteria suggest a lag length of 1.
